Investigating the Applications and Limits of Single Asymmetric Particle Light Scattering using Limited Detection Schemes

### 2022-11-15 Manuscript_rev1.tex
Add files via upload

\subsection{Brownian Simulation}
\label{sec:2.1}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Orientation estimation from scattering measurements}
\label{sec:2.2}

We represent the instantaneous orientation of the moving dimer in the
trap as a unit vector $\hat{\bf s}$, pointing from the centre of the
larger sphere to the centre of the smaller sphere.  A plane wave
``probe'' laser beam directed perpendicular to the trapping laser,
incident on the dimer, generates a scattering pattern dependent on the
dimer's instantaneous orientation, $I(\bar{\bf s},\theta_k)$.  This
scattering pattern was computed using MSTM for each time step of the
Brownian dynamics simulation.  To represent a simulated measurement,
three angles ($\theta_1$, $\theta_2$, $\theta_3$) were chosen, and the
calculated intensity at each angle $\theta_k$ is recorded as
$I(\hat{\bf s}, \theta_k)$.

Our goal is to estimate the dimer orientation $\bar{\bf s}$ over time,
based on the scattering measurements $I(\bar{\bf s},\ \theta_k)$: the
question then is what set of angles ($\theta_1$, $\theta_2$,
$\theta_3$) give us the most useful information on $\hat{\bf s}$.  To
initially simplify the problem, rather than trying to get an exact
estimation of $\hat{\bf s}$, we discretise the orientation into
$n_{\rm ref}=30$ possible reference orientations $\hat{\bf n}_\alpha$
that are evenly distributed on the unit sphere \cite{Rey2006}.
%
We then consider how to optimise an experiment to identify the
reference orientation $\hat{\bf n}_\alpha$ that is closest to the
actual orientation $\hat{\bf s}$ of the dimer.
%
The method can be extended to an arbitrarily large number of reference
orientations, but for clarity and practicability we use a relatively
small number here; additionally, the choice of a small number of
discrete reference or ``candidate'' orientations also accounts for the
fact that any experiment will necessarily have a limited precision.
%
Using MSTM we compute the scattering that would be produced by the
dimer in each of the reference orientations, denoted as
$I(\hat{\bf n}_\alpha, \theta)$ and obtain ``measurements''
$I(\hat{\bf n}_\alpha, \theta_k)$ at our chosen set of angles
($\theta_1$, $\theta_2$, $\theta_3$).
%
These raw intensities are normalised according to
\begin{align}
\label{eq:scale}
  y_k(\hat{\bf n}_\alpha)
  = 
  \frac{I(\hat{\bf n}_\alpha, \theta_k) - \langle I(\hat{\bf n},\theta_k) \rangle } 
  {\langle I^2(\hat{\bf n},\theta_k) \rangle -\langle I(\hat{\bf n}, \theta_k)\rangle^2}
\end{align}
where the denominator is simply the standard deviation for our values
of $I(\hat{\bf n}, \theta_k)$.  The dimer's \emph{actual}
instantaneous scattered intensity, based on the real instantaneous
orientation $\bar{\bf s}$, is similarly scaled using
Eq.~\eqref{eq:scale} to give $y_1(\bar{\bf s})$, $y_2(\bar{\bf s})$,
and $y_k(\bar{\bf s})$.
%
The reference orientations, raw intensities, and scaled signals are
given in Tables~\ref{tab:A1} and \ref{tab:A2}.
%
In practice, $y_k(\bar{\bf s})$ will have an inherent amount of
uncertainty in our measurement due to noise from our detector.  We
compare our instantaneous signal to our reference signal by assuming
that the measurement uncertainty for each detection fibre is Gaussian
and is centred about $y_k(\bar{\bf s})$.
%
Combining all three detection angles provides us with the conditional
probability that, should the dimer be in orientation
$\hat{\bf n}_\alpha$, it would produce a signal ($y_1$, $y_2$, $y_3$):
\begin{align}
\label{eq:conditional}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  = \prod^3_{k=1}
(2\pi\sigma_k^2)^{-1/2} 
e^{-(y_{k}-y_{k}(\hat{\bf n}_\alpha))^2/2\sigma_k^2}
\end{align}
where $\sigma_k$ is related to the uncertainty in the detected signal
from our dimer $y_k(\bar{\bf s})$.  We left this as a tuneable
parameter to characterize the influence of experimental error on our
predictive method.  The signal error was simulated in our model by
stochastically adjusting our values of $y_k(\bar{\bf s})$.
\begin{eqnarray*}
  \sigma_k
  &= \epsilon\bar{y}(\hat{\bf n}_k)
  \\
  \Rightarrow y(\bar{\bf s}_k) &= y(\bar{\bf s})_k \pm n\sigma_k
  \\ 
n \in \mathbb{R}, n\in[0,1]
\end{eqnarray*} 
where $\epsilon$ is the percent error expected from our detection
fibres.  Equation~\eqref{eq:conditional} assigns a probability to each
reference orientation based on how similar the ``reference orientation
signal'' $y_{k}(\hat{\bf n}_\alpha)$ is to the actual signal
$y_{k}(\bar{\bf s})$ generated by the dimer in its real orientation
$\bar{\bf s}$.  However, if our values of $y_k(\hat{\bf n}_\alpha)$
are similar to one another, the probability distribution from
Eq.~\eqref{eq:conditional} will therefore assign similar probability
for multiple reference orientations.  Bayesian inference allows one to
update a probability distribution by accounting for information known
prior to making a measurement.  We apply this by accounting for our
distribution of reference orientations and instantaneous signals.
\begin{align}
  \label{eq:bayes}
  p(\hat{\bf n}_\alpha| y_1,y_2,y_3)
  &=
    \frac{p(y_1,y_2,y_3|\hat{\bf n}_\alpha)
    p(\hat{\bf n}_\alpha)}{p(y_1, y_2, y_3)}
\end{align}
where $p(\hat{\bf n}_\alpha)$ and $p(y_1, y_2, y_3)$ are the prior
estimates of the distributions of particle orientations and
instantaneous signals, respectively.  The former can be estimated by
some Boltzmann distribution based on how far apart reference
orientations are in physical space, covered in Section~\ref{sec:2.3}.
The latter prior $p(y)$ is the probability of our dimer producing a
signal $y_k(\bar{\bf s})$ that falls with our distribution of
reference signals $y_k(\hat{\bf n})$.  This is given by taking the
discrete integral over collection of reference orientations.
\begin{align}
  p(y_1, y_2, y_3)
  =
  \sum_{\alpha=1}^{n_{\rm ref}}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  p(\hat{\bf n}_\alpha)
\end{align}
The implementation of Eq.~\eqref{eq:bayes} improves our estimate by
suppressing reference orientations that are far away from our dimer's
orientation vector in physical space.  In order to evaluate the
accuracy of our method, we tested it using a Brownian dynamics
simulation of the dimer (see Section~\ref{sec:2.1}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Testing the Model}
\label{sec:2.3}

Using our simulation from Section~\ref{sec:2.1} we calculated the
instantaneous signal from our dimer at each time step using MSTM.  We
applied Eq.~\eqref{eq:bayes} --- covered in Section~\ref{sec:2.2} ---
and the reference orientation with the highest probability is taken as
our estimation of the dimer's instantaneous orientation.  The prior of
the reference orientations $p(\hat{\bf n}_\alpha)$ is defined at each
time step by accounting for the physical distance between the previous
estimate $\hat{\bf n}_{\alpha}(t - \Delta t)$ and each reference
orientation $\hat{\bf n}_\alpha$
\begin{align}
  r_i(t, \hat{\bf n}_\alpha)
  &= \frac{1}{2}((\hat{\bf n}_{\alpha}(t) \cdot \hat{\bf n}_{t-\Delta t})-1)
  \\
  p_i(\hat{\bf n})
  &= \frac{e^{\beta (r_i(t,\hat{\bf n}_i)-1)}}
{\sum_{j=1}^{n_{\rm ref}}e^{\beta(r_j(t, \hat{\bf n}_\alpha)-1)}}
\end{align}
where $\beta$ is a weighting factor that controls the significance of
our priori estimate.  The simulation data from Section~\ref{sec:2.1}
was used to check if the estimation was correct by comparing the
estimate provided by Eq.~\eqref{eq:bayes} to the reference orientation
closest to the instantaneous orientation, denoted as
$\hat{\bf n}_{best}$.  To measure the error in the model's estimate
the distribution's of $p(\hat{\bf n}| y(\bar{\bf s}))$ and an
ideal result, $p_ideal$, were compared.  An ideal distribution is one
that is 0 for every $\hat{\bf n}$ apart from the correct result.
\begin{align}
p_{ideal} = 
\begin{cases}
	1 & \text{when $\hat{\bf n}_\alpha$ = $\hat{\bf n}_{best}$}\\
	0 & \text{anywhere else}
\end{cases}
\end{align}
The distribution from Eq.~\eqref{eq:bayes} will assign some non-zero
probability to every reference orientation.  The model's error was
measured by calculating the Kullback-Leibler divergence $K_l$ between
the two distributions
\begin{align}
  K_{l, \#}(p(\hat{\bf n}_\alpha| y_1, y_2, y_3), p_{ideal})
  =\nonumber
  \\
&p_{ideal}\ln \left[\frac{p_{ideal}}{p(\hat{\bf n}_{best}| y_1,y_2,y_3))}
\right]
\end{align}
where a more negative value of $K_l$ indicates a poorer estimation of
the dimer's instantaneous orientation.  By summing the divergence of
each measurement across the entire simulation we get an evaluation of
how well the model performed in estimating the dimer's orientation.
To compare between different iterations of our model the we compare
our result of $K_l$ to a worst case scenario and evaluate how much it
improves upon this, denoted as $F(K_l)$:
\begin{align}
K_{l, \ total} &= \sum\limits_{\# =1}^{timesteps} K_{l,\#} \\
K_{l, \ worst} &= -\sum\limits_{\#=1}^{timesteps} \ln \left[\frac{1}{1/30} \right] \\
F(K_l) &= \frac{K_{l,\ worst}}{K_{l, \ total}}
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optimization of parameters}
\label{sec:2.4}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Asymmetric dimer dynamics}
\label{sec:3.1}

@@

\begin{figure}[h]
	\label{fig:motion}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width =\textwidth]{./Images/traj.png}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/pos.png}
	\end{subfigure}
	\caption{Simulation results of: a) the dimers orientation vector with time, b) the dimer's [x,y,z] position with time.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Impact of signal error on model predictions}
\label{sec:3.2}

@@

	\centering
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[width=\textwidth]{./Images/epsilon_5.png}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[width=\textwidth]{./Images/epsilon_15.png}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\includegraphics[width=\textwidth]{./Images/epsilon_25.png}
	\end{subfigure}
	\caption{Model prediction for signal error of a) $5\%$, b) $15\%$, and c) $25\%$. Blue line denotes the best result we can achieve, orange line denotes the result provided by eq~\ref{eq:bayes}}
	\label{fig:epsilon}
\end{figure}

@@

\begin{figure}
	\label{fig:beta}
	\centering
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[width=\textwidth]{./Images/beta_5.png}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[width=\textwidth]{./Images/beta_6.png}
	\end{subfigure}
	\caption{Model prediction for signal error of $25\%$ when a) $\beta = 5$ and b) $\beta=6$}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Parameter Optimisation Results}
\label{sec:3.3}

@@

\begin{figure}[h]
	\label{fig:corner}
	\centering
	\includegraphics[width=0.45\textwidth]{./Images/corneranglesfreed-1.png}
	\caption{Corner plot mapping combinations of $\theta$ that generate the best improvement}
\end{figure}

@@

As covered in Section~\ref{sec:3.2} our choice for beta can help to
improve our estimation by restricting it in the physical space. In
addition depending on our choice of angles we are also setting the
lower limit for our signal error $\epsilon$, so it may be preferable
to choose a selection of angles that allows for a large signal error
and then adjust the weighting factor to improve upon our estimation.

>>>>

\subsection{Brownian Simulation}
\label{sec:brownian}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Orientation estimation from scattering measurements}
\label{sec:Bayes}

We consider our dimer from Section~\ref{sec:brownian} in an optical trap; at any point in time we can draw a unit vector $\hat{s}$ that points from the centre of larger sphere, to the centre of the smaller sphere. A plane wave 'probe' laser, directly perpendicular to the trapping laser, is incident on the dimer generating a scattering pattern that is dependent upon the dimer's orientation $I(\hat{\bf s}, \theta)$, computed using MSTM. To represent the experimental set up, three angles  ($\theta_1, \ \theta_2, \ \& \theta_3$) were chosen and the calculated intensity at each angle $\theta_k$ was recorded as $I(\hat{s}, \theta_k)$

Our goal is to determine the orientation of our trapper dimer based on the scattering measurements $I(\hat{n}, \ \theta_k)$ collected from three detection fibres situated at $\theta_1,\ \theta_2, \ \& \ \theta_3$. Rather than get an exact estimate of the dimer's orientation the possible orientation space is discretised into $\textit{n}_ref \ = \ 30$ possible reference orientations $\hat{\bf n}_{\alpha}$ that are evenly distributed on a unit sphere \cite{Rey2006}. Using MSTM we compute the raw intensities that would be collected from the dimer in each reference orientation $I(\hat{\bf n}_{\alpha}, \theta_k)$. 
%
These raw intensities are normalised according to
\begin{align}
\label{eq:scale}
  y_k(\hat{\bf n}_\alpha)
  = 
  \frac{I(\hat{\bf n}_\alpha, \theta_k) - \langle I(\hat{\bf n},\theta_k) \rangle } 
  {\langle I^2(\hat{\bf n},\theta_k) \rangle -\langle I(\hat{\bf n}, \theta_k)\rangle^2}
\end{align}
where the denominator is simply the standard deviation for our values
of $I(\hat{\bf n}, \theta_k)$.

The reference orientations, raw intensities, and scaled signals are given in Tables~\ref{tab:A1} and \ref{tab:A2}.
%
In practice, $y_k(\bar{\bf s})$ will have an inherent amount of
uncertainty in our measurement due to noise from our detector.  We can compare any instantaneous signal $y_1, y_2, y_3$ to our reference signals by assuming that the measurement uncertainty for each detection fibre is Gaussian and is centred about $y_k(\bar{\bf n})$.
%
Combining the signals from all three detection angles provides us with the conditional probability that, should the dimer be in orientation
$\hat{\bf n}_\alpha$, it would produce a signal ($y_1$, $y_2$, $y_3$):
\begin{align}
\label{eq:conditional}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  = \prod^3_{k=1}
(2\pi\sigma_k^2)^{-1/2} 
e^{-(y_{k}-y_{k}(\hat{\bf n}_\alpha))^2/2\sigma_k^2}
\end{align}
where $\sigma_k$ is related to the uncertainty in the detected signal
from our dimer $y_k(\bar{\bf s})$.

We left this as a tuneable parameter to characterize the influence of experimental error on our predictive method.  The signal error was simulated in our model by stochastically adjusting our values of $y_k(\bar{\bf s})$.
\begin{eqnarray*}
  \sigma_k&=\epsilon\bar{y}(\hat{\bf n}_k)
  \\
  \Rightarrow y(\bar{\bf s}_k)&=y(\bar{\bf s})_k \pm n\sigma_k
  \\ 
n \in \mathbb{R},&n\in[0,1]
\end{eqnarray*} 
where $\epsilon$ is the percent error expected from our detection
fibres.

Equation~\eqref{eq:conditional} gives the probability that a signal
($y_1$, $y_2$, $y_3$) will be measured if a dimer is in reference
orientation $\hat{\rm n}_\alpha$.
%
Using Bayes' theorem, the probability that the dimer is in reference
orientation $\hat{\bf n}_\alpha$, given that the signal ($y_1$, $y_2$,
$y_3$) is measured, can be estimated:
%.
\begin{align}
  \label{eq:bayes}
  p(\hat{\bf n}_\alpha| y_1,y_2,y_3)
  &=
    \frac{p(y_1,y_2,y_3|\hat{\bf n}_\alpha)
    p(\hat{\bf n}_\alpha)}{p(y_1, y_2, y_3)}
\end{align}
where $p(\hat{\bf n}_\alpha)$ and $p(y_1, y_2, y_3)$ are the prior
estimates of the distributions of particle orientations and
instantaneous signals, respectively.
%
Without any prior evidence we assume that the orientation priori of our dimer $p(\hat{\bf n}_{\alpha})$ is uniform. Knowledge of the dimer from previous measurement can be used to inform our estimate of $p(\hat{\bf n}_{\alpha})$ covered in Section~\ref{sec:test}.  The latter prior $p(y)$ is the probability of measuring a signal ($y_1$, $y_2$, $y_3$).  This is given by taking the discrete integral over collection of reference orientations.
\begin{align}
  p(y_1, y_2, y_3)
  =
  \sum_{\alpha=1}^{n_{\rm ref}}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  p(\hat{\bf n}_\alpha)
\end{align}
From \eqref{eq:bayes} we get a mass probability distribution that denotes the probability that our dimer is in orientation $\hat{\bf n}_{\alpha}$ given a signal ($y_1$, $y_2$, $y_3$). In order to evaluate the accuracy of our method, we tested it using a Brownian dynamics simulation of the dimer (see Section~\ref{sec:brownian}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Calculation of error}
\label{sec:divergence}
Section~\ref{sec:Bayes} covered how Bayes theorem can be applied to estimate the orientation of a dimer based on its scattering signal. To evaluate the estimation we can use the simulation in Section~\ref{sec:brownian}; we denote the dimer's \emph{actual} orientation as $\hat{\bf s}$ and use MSTM to calculate its light scattering $I(\hat{\bf s}, \theta)$. At each angle $\theta_k$ we use \eqref{eq:scale} to scale the measurements collected from our dimer and record them as $y_1(\hat{\bf s})$, $y_2(\hat{\bf s})$, $y_3(\hat{\bf s})$. These measurements signals are used to calculate $p(\hat{\bf n}_{\alpha}\parallel y_1, y_2, y_3)$, because we know $\hat{s}$ we can determine which reference orientation is closest, denoted as $\hat{\bf n}_{best}$
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Testing the Model}
\label{sec:test}

Using our simulation from Section~\ref{sec:brownian} we calculated the
instantaneous signal from our dimer at each time step using MSTM.  We
applied Eq.~\eqref{eq:bayes} --- covered in Section~\ref{sec:Bayes} ---
and the reference orientation with the highest probability is taken as
our estimation of the dimer's instantaneous orientation.  The prior of
the reference orientations $p(\hat{\bf n}_\alpha)$ is defined at each
time step by accounting for the physical distance between the previous
estimate $\hat{\bf n}_{\alpha}(t - \Delta t)$ and each reference
orientation $\hat{\bf n}_\alpha$
\begin{align}
  r_i(t, \hat{\bf n}_\alpha)
  &= \frac{1}{2}((\hat{\bf n}_{\alpha}(t) \cdot \hat{\bf n}_{t-\Delta t})-1)
  \\
  p_i(\hat{\bf n})
  &= \frac{e^{\beta (r_i(t,\hat{\bf n}_i)-1)}}
{\sum_{j=1}^{n_{\rm ref}}e^{\beta(r_j(t, \hat{\bf n}_\alpha)-1)}}
\end{align}
where $\beta$ is a weighting factor that controls the significance of
our priori estimate. The simulation data from Section~\ref{sec:brownian}
was used to check if the estimation was correct by comparing the
estimate provided by Eq.~\eqref{eq:bayes} to the reference orientation
closest to the instantaneous orientation, denoted as
$\hat{\bf n}_{best}$.  To measure the error in the model's estimate
the distribution's of $p(\hat{\bf n}| y(\bar{\bf s}))$ and an
ideal result, $p_ideal$, were compared.  An ideal distribution is one
that is 0 for every $\hat{\bf n}$ apart from the correct result.
\begin{align}
p_{ideal} = 
\begin{cases}
	1 & \text{when $\hat{\bf n}_\alpha$ = $\hat{\bf n}_{best}$}\\
	0 & \text{anywhere else}
\end{cases}
\end{align}
The distribution from Eq.~\eqref{eq:bayes} will assign some non-zero
probability to every reference orientation.  The model's error was
measured by calculating the Kullback-Leibler divergence $K_l$ between
the two distributions
\begin{align}
  K_{l, \#}(p(\hat{\bf n}_\alpha| y_1, y_2, y_3), p_{ideal})
  = p_{ideal}\ln \left[\frac{p_{ideal}}{p(\hat{\bf n}_{best}| y_1,y_2,y_3))}
\right]
\end{align}
where a more negative value of $K_l$ indicates a poorer estimation of
the dimer's instantaneous orientation.  By summing the divergence of
each measurement across the entire simulation we get an evaluation of
how well the model performed in estimating the dimer's orientation.
To compare between different iterations of our model the we compare
our result of $K_l$ to a worst case scenario and evaluate how much it
improves upon this, denoted as $F(K_l)$:
\begin{align}
K_{l, \ total} &= \sum\limits_{\# =1}^{timesteps} K_{l,\#} \\
K_{l, \ worst} &= -\sum\limits_{\#=1}^{timesteps} \ln \left[\frac{1}{1/30} \right] \\
F(K_l) &= \frac{K_{l,\ worst}}{K_{l, \ total}}
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optimization of parameters}
\label{sec:ultranest}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Asymmetric dimer dynamics}
\label{sec:motion}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width =\textwidth]{./Images/traj.png}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/pos.png}
	\end{subfigure}
	\caption{Simulation results of: a) the dimers orientation vector with time, b) the dimer's [x,y,z] position with time.}
	\label{fig:motion}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Impact of signal error on model predictions}
\label{sec:epsilon}

@@

	\centering
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\textwidth]{./Images/epsilon_at_5.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\textwidth]{./Images/epsilon_at_15.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\textwidth]{./Images/epsilon_at_25.png}
	\end{subfigure}
	\caption{Model prediction for signal error of a) $5\%$, b) $15\%$, and c) $25\%$. Blue line denotes the best result we can achieve, orange line denotes the result provided by eq~\ref{eq:bayes}}
	\label{fig:epsilon}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.33\textwidth}
		\includegraphics[width=\textwidth]{./Images/Beta_2.png}
	\end{subfigure}
	\begin{subfigure}{0.33\textwidth}
		\includegraphics[width=\textwidth]{./Images/Beta_3.png}
	\end{subfigure}
	\caption{Model prediction for signal error of $25\%$ when a) $\beta = 5$ and b) $\beta=6$}
	\label{fig:beta}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{Parameter Optimisation Results}
\label{sec:ultranest_res}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{./Images/corneranglesfreed-1.png}
	\caption{Corner plot mapping combinations of $\theta$ that generate the best improvement}
	\label{fig:corner}
\end{figure}

@@

As covered in Section~\ref{sec:epsilon} our choice for beta can help to
improve our estimation by restricting it in the physical space. In
addition depending on our choice of angles we are also setting the
lower limit for our signal error $\epsilon$, so it may be preferable
to choose a selection of angles that allows for a large signal error
and then adjust the weighting factor to improve upon our estimation.
